### 2018-03-17 paper/7-related.tex
Fix typo

\begin{minted}[xleftmargin=10pt]{haskell}
data Key = A Integer | B Integer | D Integer Integer deriving Ord
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
editDistance :: Task Monad Key Integer
editDistance _     (D i 0) = Just $ pure i
editDistance _     (D 0 j) = Just $ pure j
editDistance fetch (D i j) = Just $ do
    ai <- fetch (A i)
    bj <- fetch (B i)
    if ai == bj
        then fetch (D (i - 1) (j - 1))
        else do
            insert  <- fetch (D  i      (j - 1))
            delete  <- fetch (D (i - 1)  j     )
            replace <- fetch (D (i - 1) (j - 1))
            return (1 + minimum [insert, delete, replace])
editDistance _ _ = Nothing
\end{minted}

@@

>>>>

\begin{minted}[xleftmargin=10pt]{haskell}
data Key = A Integer | B Integer | D Integer Integer deriving Ord
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
editDistance :: Task Monad Key Integer
editDistance _     (D i 0) = Just $ pure i
editDistance _     (D 0 j) = Just $ pure j
editDistance fetch (D i j) = Just $ do
    ai <- fetch (A i)
    bj <- fetch (B j)
    if ai == bj
        then fetch (D (i - 1) (j - 1))
        else do
            insert  <- fetch (D  i      (j - 1))
            delete  <- fetch (D (i - 1)  j     )
            replace <- fetch (D (i - 1) (j - 1))
            return (1 + minimum [insert, delete, replace])
editDistance _ _ = Nothing
\end{minted}

@@

Self-adjusting computation, memoization and build systems are inherently related
topics, which poses the question of whether there is an underlying common
abstraction waiting to be discovered.
